IWOCA Paper

### 2018-01-03 paper/paper.tex
added bibliography

\documentclass{llncs}

@@

The bin packing problem is a widely researched problem\\
BPP can be stated as follows:

\begin{itemize}
	\item \textcolor{red}{original BPP}
	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
	\item Combinatorial NP-hard problem (computational complexity)
	\item NP-Complete (decision problem)
	\item Heuristics
	\item FF and FFD
	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki)
	\item ``bound for FFD is tight'' (wiki)
	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)

@@

>>>>

\documentclass[oribibl]{llncs}

@@

The one-dimensional bin packing problem (BPP) is a widely researched problem \\
The problem is as follows: given a set of $n$ weighted items  and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items. NP-Hard \cite{garey1979}, \cite{coffman1984}, \cite{lewis2017}, \cite{becker2015}, \cite{becker2010}, \cite{goulimis2004}, \cite{karp1972}, \cite{mahadev1995}.

\begin{itemize}
	\item \textcolor{red}{original BPP}
	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
	\item Combinatorial NP-hard problem (computational complexity) Gary and Johnson 1979
	\item NP-Complete (decision problem)
	\item Heuristics
	\item FF and FFD
	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki)
	\item ``bound for FFD is tight'' (wiki)
	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)

@@

\bibliographystyle{dcu}
\bibliography{includes/bibliography}

%\input{includes/bibliography.tex}
